### 2024-04-08 manuscript.Rmd
update dimensions of figures

<!-- Fig. Vertebral counts vs max body length  -->
```{r fig-tbl-vert, fig.cap= 'Maximum vertebral counts plotted against maximum total body length for Australian typhlopids. Trend line represent PGLS regression for Australian species.', out.width="165mm", out.height= "126mm"}

@@

<!-- Fig: Pleomerism and ratio correlations -->
```{r fig-vert-aspect-ratios, fig.cap= 'Relationship between mean vertebrae and aspect ratios among Australian blindsnake species. Vertebrae ratio is calculated by total vertebrae/total length, and aspect ratio is total body length/midbody diameter. Species with large aspect ratios are narrow-and-long while species with low aspect ratios robust-and-wide.', out.width="165mm", out.height= "180mm"}

@@

<!-- Fig: Vertebral profile -->
```{r fig-vertebral-profile, fig.cap= 'Relative vertebral length plotted against vertebra number for three example species with fitted 4° polynomial curves overlaid.', out.width="126mm", out.height= "160mm"}

@@

## Miscellaneous 
Traditionally, ventral scale counts have been used as a proxy for vertebral number as they correlate for most alethinophidian snakes [@alexanderPattern1966]. We found that this is (not) the case in blindsnakes. Blindsnakes are generally small enough to fit in an X-ray scanner so more people should do it.

>>>>

<!-- Fig. Vertebral counts vs max body length  -->
```{r fig-tbl-vert, fig.cap= 'Maximum vertebral counts plotted against maximum total body length for Australian typhlopids. Trend line represent PGLS regression for Australian species.', out.width="165mm", out.height= "124mm"}

@@

<!-- Fig: Pleomerism and ratio correlations -->
```{r fig-vert-aspect-ratios, fig.cap= 'Relationship between mean vertebrae and aspect ratios among Australian blindsnake species. Vertebrae ratio is calculated by total vertebrae/total length, and aspect ratio is total body length/midbody diameter. Species with large aspect ratios are narrow-and-long while species with low aspect ratios robust-and-wide.', out.width="165mm", out.height= "124mm"}

@@

<!-- Fig: Vertebral profile -->
```{r fig-vertebral-profile, fig.cap= 'Relative vertebral length plotted against vertebra number for three example species with fitted 4° polynomial curves overlaid.', out.width="140mm", out.height= "197mm"}

@@

## Miscellaneous 
Traditionally, ventral scale counts have been used as a proxy for vertebral number as they correlate for most alethinophidian snakes [@alexanderPattern1966]. We found that this is (not) the case in blindsnakes. Blindsnakes are generally small enough to fit in an X-ray scanner, so more people should do it.
